Influences of GDP in the United States

### 2022-12-09 Manuscript/manuscript.tex
commit

\section*{Discussion}
In practice, there are many economic indicators that impact GDP. 
There is no unique set of factors discovered yet that predict GDP. 
This paper showed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rate have a significant relationship with GDP.
These variables were selected with author subjectivity, and this is important to take into consideration. 
This paper did not show any significant relationship between Total Primary Energy Consumption or Population with GDP in the United States. 
It is also important to consider that the homoscedacity assumption of Ordinary Least Squares Regression is questionable in this paper. 
For future studies, to limit this violation the data could be transformed.
This research is a introductory study into the relationship between energy consumption and economic growth. 
Even though this study showed that there is no significant relationship between GDP and Enery Consumption, this relationship should be investigated further.
Energy is such a vital part of society in the United States, and if a relationship between GDP and Energy Consumption is found, this can be vital for economists in many counties.
This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.

>>>>

\section*{Discussion}
In practice, there are many economic indicators that impact GDP. 
There is no unique set of factors discovered yet that predict GDP. 
This paper showed that Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, and Unemployment Rate have a significant relationship with GDP.
These variables were selected with author subjectivity, and this is important to take into consideration. 
This paper did not show any significant relationship between Total Primary Energy Consumption or Population with GDP in the United States. 
It is also important to consider that the homoscedacity assumption of Ordinary Least Squares Regression is questionable in this paper. 
For future studies, to limit this violation the data could be transformed.
This research is a introductory study into the relationship between energy consumption and economic growth. 
Even though this study showed that there is no significant relationship between GDP and Enery Consumption, this relationship should be investigated further.
Energy is such a vital part of society in the United States, and if a significant relationship between GDP and Energy Consumption is found, this can be vital for economists in many counties.
This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.
